---
title: "Analysis - Gist generation"
subtitle: "Comparison of responses between lab and MTurk participants - `r format(Sys.time(), '%d %B, %Y')`"
geometry: left=2cm,right=2cm,top=2cm,bottom=2cm
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
header-includes: \usepackage{xcolor}
---

```{r include=FALSE, echo=FALSE, message=FALSE}
source('embed_import_libraries.R')
source('embed_configuration.R')

# Functions
source('function-analyse_plot_single_image.R')
source('function-aggregate_word_column.R')
source('function-calculate_kl_for_dataframe.R')
source('function-compute_kl.R')
source('function-compute_pairwise_kl.R')
source('function-image_utilities.R')
source('function-load_alon_descriptors.R')
source('function-load_data.R')
source('function-load_subject_data.R')
source('function-plot_kl_divergence.R')
source('function-plot_word_cloud.R')
source('function-utilities.R')
source('function-validate_img_soa_group_numbers.R')

library(ggrepel)
library(gridExtra)

```

## Overview

The purpose of this analysis is to compare whether the performance of MTurk participants were significantly different from the lab participants, in the gist generation experiment.

In the experiment, participant provided five words to describe their impression of the images, flashed in different SOAs - 67ms, 133ms, and 267ms. Participants completed 1 block - which contains 21 images.

## Analysis Approach

To cover all permutation of images + SOA conditions in each block, we need 30 participants. We use the same experiments and stimuli between lab and online.

In MTurk, we had collected responses from at least 30 particpants. However, in the lab, we only had 10 participants to cover a subset of the image + SOA permutations.

As a result, we will use a goodness-of-fit test to see if the performance of the 10 lab participants were significantly different from online participants.

As participants were generating words (qualitative data), we summarised the word distribution under each SOA for each image, and calculate the KL divergence between each pair of SOAs, namely between 67 and 133ms (67-133), 133 and 267ms (133-267) and 67 and 267ms (67-267).

If the conditions between lab and MTurk participants are similar, the performance of MTurk participants and lab participants should not be significantly different.

### Details

The following describes the detail step of the analysis:

* We repeated the following in 50 iterations:
  * Randonly select 10 participants out of 30 from the MTurk experiments.
  * Calculate the KL divergence values (67-133, 133-267, 67-267) in this subset of 10 participants for all the images and store them into a table.
* We created a table of 50 x 21 = 1050 rows and each image will have 50 rows of KL divergence values.
* We calculated the median of the three KL divergence groups - median_67_133, median_133_267, median_67_267.
* We calculated the KL divergence values for the same experiment for lab participants.
* We used KS-Test to determine if the KL divergence values from the lab were significantly different from the online KL divergence (median).

```{r configuration, include=FALSE}
summary_file_lb = c(
  '../../data/batch_1/gist_batch_v1_1_1_lb_summary.csv',
  '../../data/batch_1/gist_batch_v1_1_2_lb_summary.csv',
  '../../data/batch_1/gist_batch_v1_1_3_lb_summary.csv',
  '../../data/batch_1/gist_batch_v1_1_4_lb_summary.csv')

details_file_lb = c(
  '../../data/batch_1/gist_batch_v1_1_1_lb_raw-sc.csv',
  '../../data/batch_1/gist_batch_v1_1_2_lb_raw-sc.csv',
  '../../data/batch_1/gist_batch_v1_1_3_lb_raw-sc.csv',
  '../../data/batch_1/gist_batch_v1_1_4_lb_raw-sc.csv')

summary_file_mt = c(
  '../../data/batch_1/gist_batch_v1_1_1_mt_summary.csv',
  '../../data/batch_1/gist_batch_v1_1_2_mt_summary.csv',
  '../../data/batch_1/gist_batch_v1_1_3_mt_summary.csv',
  '../../data/batch_1/gist_batch_v1_1_4_mt_summary.csv')

details_file_mt = c(
  '../../data/batch_1/gist_batch_v1_1_1_mt_raw-sc.csv',
  '../../data/batch_1/gist_batch_v1_1_2_mt_raw-sc.csv',
  '../../data/batch_1/gist_batch_v1_1_3_mt_raw-sc.csv',
  '../../data/batch_1/gist_batch_v1_1_4_mt_raw-sc.csv')

```

```{r read-summary-df-file, echo=FALSE, message=FALSE, include = FALSE, warning=FALSE}

# load_raw_df <- function(summary_file, details_file, identifier) {
#   ## Perform preliminary assertion checks on the data integrity
#   summary_details_list <- validate_img_soa_group_numbers(summary_file, details_file,
#                                                          expected_group_number = 0,
#                                                          expected_image_number = 0,
#                                                          enforce_validation = FALSE)
#   summary_df <- summary_details_list$summary
#   details_df <- summary_details_list$details
# 
#   full_raw_df <- load_data(summary_file, details_file, by_subject = TRUE)
#   full_raw_df$soa = as.factor(full_raw_df$soa)
#   full_raw_subject_df <- load_subject_data(summary_file, details_file)
# 
#   full_df <- copy(full_raw_df) # This will be manipulated by reference so reassign to another variable.
#   all_df <- unique(full_df[,-c("subject", "trialnum", "group")][, `:=`(frequency = sum(frequency), confidence = mean(confidence)), by = c("img", "soa", "word", "img_id")])
# 
#   master_raw_df <- full_df[, c("img_id", "soa", "subject", "word", "frequency", "confidence")]
#   master_raw_df <- cbind(master_raw_df, experiment_no = identifier)
#   return(master_raw_df)
# }
# 
# lab_raw_df = data.table()
# for (i in 1:length(summary_file_lb)) {
#   lab_raw_df <- rbind(lab_raw_df, load_raw_df(summary_file_lb[i], details_file_lb[i], i))
# }
# lab_raw_stem_df <- cbind(lab_raw_df, stem_word = stem_words(lab_raw_df$word)$stem_word)
# 
# mt_raw_df = data.table()
# for (i in 1:length(summary_file_mt)) {
#   mt_raw_df <- rbind(mt_raw_df, load_raw_df(summary_file_mt[i], details_file_mt[i], i))
# }
# mt_raw_stem_df <- cbind(mt_raw_df, stem_word = stem_words(mt_raw_df$word)$stem_word)

load('analysis_compare_lab_online.RData')

## Exclude two lab members (2)
lab_raw_df <- lab_raw_df[as.integer(subject) > 100]
lab_raw_stem_df <- lab_raw_stem_df[as.integer(subject) > 100]
```


## Results

### Comparison of confidence ratings

```{r echo=FALSE, message=TRUE, warning=FALSE, echo=FALSE}
## Plot both confidence intervals

theme_set(theme_cowplot())

confidence_lab_df <- copy(lab_raw_df)
confidence_lab_df <- confidence_lab_df[experiment_no == 1]
confidence_lab_df$soa <- as.factor(confidence_lab_df$soa)
confidence_lab_df$img_id <- as.factor(confidence_lab_df$img_id)
confidence_lab_df$confidence <- as.factor(confidence_lab_df$confidence)

confidence_mt_df <- copy(mt_raw_df)
confidence_mt_df <- confidence_mt_df[experiment_no == 1]
confidence_mt_df$soa <- as.factor(confidence_mt_df$soa)
confidence_mt_df$img_id <- as.factor(confidence_mt_df$img_id)
confidence_mt_df$confidence <- as.factor(confidence_mt_df$confidence)

# Combined confidence
confidence_lab_plot_df <- confidence_lab_df[soa != "Unlimited", .(count = sum(frequency)), by = c("soa", "confidence")][, .(soa, confidence, count, percentage = count*100/sum(count))]

plab_1 <- ggplot(confidence_lab_plot_df, 
                 aes(x = soa, 
                     y = percentage,
                     fill = confidence)) +
  #geom_histogram(stat = "identity") +
  geom_bar(position = 'fill', stat = 'identity') + 
  xlab("Presentation Duration") +
  ylab("Percentage (%)") +
  scale_y_continuous(expand = c(0, 0), labels = function(x) paste0(x*100)) +
  ggtitle(paste0("Lab (N=", length(unique(confidence_lab_df$subject)), ")"))+ 
  theme(legend.text = element_text(size=16), axis.text = element_text(size = 22), plot.title = element_text(size = 20)) +
  scale_fill_brewer(palette="Paired",name = "Confidence Rating", 
                  labels = c("Don't know", "Guess", "Maybe", "Confident", "Very Confident"))

# plab_2 <- ggplot(confidence_lab_df[soa != "Unlimited"], aes(x = img_id, fill = confidence)) +
#   geom_histogram(stat = "count", position = "fill") +
#   xlab("Image") +
#   ylab("Confidence Ratings Proportion") +
#   scale_fill_grey(start = 0, end = .9, 
#                   name = "Confidence", 
#                   labels = c("Don't know", "Guess", "Maybe", "Confident", "Very Confident")) +
#   theme(axis.text = element_text(size = 10), axis.text.x = element_text(angle = 90, vjust = 1))

confidence_mt_plot_df <- confidence_mt_df[soa != "Unlimited", .(count = sum(frequency)), by = c("soa", "confidence")][, .(soa, confidence, count, percentage = count*100/sum(count))]

pmt_1 <- ggplot(confidence_mt_plot_df, aes(x = soa, y = percentage, fill = confidence)) +
  geom_bar(position = 'fill', stat = 'identity') + 
  xlab("Presentation Duration") +
  ylab("Percentage (%)") +
  scale_y_continuous(expand = c(0, 0), labels = function(x) paste0(x*100)) +
  ggtitle(paste0("Online (N=", length(unique(confidence_mt_df$subject)), ")"))+ 
  theme(legend.text = element_text(size=16), axis.text = element_text(size = 22), plot.title = element_text(size = 20)) +
  scale_fill_brewer(palette="Paired", name = "Confidence Rating", 
                  labels = c("Don't know", "Guess", "Maybe", "Confident", "Very Confident"))

# pmt_2 <- ggplot(confidence_mt_df[soa != "Unlimited"], aes(x = img_id, fill = confidence)) +
#   geom_histogram(stat = "count", position = "fill") +
#   xlab("Image") +
#   ylab("Confidence Ratings Proportion") +
#   scale_fill_grey(start = 0, end = .9, 
#                   name = "Confidence", 
#                   labels = c("Don't know", "Guess", "Maybe", "Confident", "Very Confident")) +
#   theme(axis.text = element_text(size = 10), axis.text.x = element_text(angle = 90, vjust = 1))

g_all <- grid.arrange(
 plab_1, pmt_1, 
 #plab_2, pmt_2,
  nrow = 1, ncol = 2)

h <- 8
ar <- 1.5
ggsave(g_all, height=h, width= h*ar, filename = "comparison-lab-online-confidence.png")

# Perform model comparison between lab and online

combine_conf_df <- rbind(confidence_lab_df[, .(img_id, soa, subject, confidence, type = "lab")], 
                        confidence_mt_df[, .(img_id, soa, subject, confidence, type = "online")])
combine_conf_df$confidence <- as.numeric(combine_conf_df$confidence)

lme_full <- lmer(confidence ~ 1 + soa + type + (soa * type) + (1|img_id) + (1 | subject), data = combine_conf_df, REML = FALSE)
lme_full_no_interact <- lmer(confidence ~ 1 + soa + type + (1|img_id) + (1 | subject), data = combine_conf_df, REML = FALSE)
lme_no_type <- lmer(confidence ~ 1 + soa + (1|img_id) + (1 | subject), data = combine_conf_df, REML = FALSE)
lme_no_type_soa <- lmer(confidence ~ 1 + (1|img_id) + (1 | subject), data = combine_conf_df, REML = FALSE)

anova(lme_full, lme_full_no_interact, lme_no_type, lme_no_type_soa, type = "LRT")

summary(lme_no_type)


AIC(lme_full, lme_full_no_interact, lme_no_type, lme_no_type_soa)
BIC(lme_full, lme_full_no_interact, lme_no_type, lme_no_type_soa)


lme_no_type_no_sbj <- lmer(confidence ~ 1 + soa + (1|img_id), data = combine_conf_df, REML = FALSE)
lme_no_type_no_img <- lmer(confidence ~ 1 + soa + (1|subject), data = combine_conf_df, REML = FALSE)

anova(lme_no_type, lme_no_type_no_sbj, lme_no_type_no_img, type = "LRT")
AIC(lme_no_type, lme_no_type_no_sbj, lme_no_type_no_img)
BIC(lme_no_type, lme_no_type_no_sbj, lme_no_type_no_img)

```

```{r include = FALSE}

## Boot-strapping function

# This function will randomly select the _sample_per_iteration_ from the data set based on exp_id
# and calculate the KL divergence between the SOA 67, 133 and 267.

calculate_rnd_kl_divergence <- function(df, exp_id, sample_per_iteration) {
  
  df <- df[experiment_no == exp_id]
  subject_list <- unique(df$subject)
  sample_subjects <- sample(subject_list, sample_per_iteration, replace = FALSE)
  sub_df <- df[subject %in% sample_subjects, ]

  kl_df <- calculate_kl_for_dataframe(sub_df, TRUE)

  sub_df <- sub_df[, .(soa_single_word_freq = sum(frequency)), by = c("img_id", "soa", "word")]
  sub_df <- sub_df[, soa_total_words := sum(soa_single_word_freq), by = c("img_id", "soa")]
  sub_df <- sub_df[, .(word_soa_proportion = soa_single_word_freq/soa_total_words, frequency = soa_single_word_freq), by = c("img_id", "soa", "word")]

  img_soa <- unique(sub_df[!img_id %in% c(3, 9, 14), .N, by = c("img_id", "soa")][order(img_id)])
  kl_divergence_df = data.table()

  for (ri in unique(img_soa$img_id)) {
      current_img_id = ri

      t <- sub_df[img_id == current_img_id, .(img_id, soa, word, word_soa_proportion, frequency)]
      #t <- t[!word %in% c("na", "none", "nothing", "nada", "dont-know", "-")]
      t$soa <- as.factor(t$soa)

      word_freq_factor <- reorder(t$word, t$frequency, sum)
      word_freq_factor_df <- data.table(word = as.vector(names(attr(word_freq_factor, "scores"))), frequency = as.vector(unname(attr(word_freq_factor, "scores"))))

      word_prop_df <- copy(t)
      word_prop_df <- word_prop_df[, .(soa_single_word_freq = sum(frequency)), by = c("img_id", "soa", "word")]
      word_prop_df <- word_prop_df[, soa_total_words := sum(soa_single_word_freq), by = c("img_id", "soa")]
      word_prop_df <- word_prop_df[, .(word_soa_proportion = soa_single_word_freq/soa_total_words), by = c("img_id", "soa", "word")]

      ggtitleimg <- function(title, imgid, soa, kl) {
        return(ggtitle(paste0(title, ' (Image ', imgid, ', SOA = ', soa, ', KL = ', sprintf("%.2f", kl), ')')))
      }

      kl_67_133 <- compute_kl(NULL, word_prop_df, c("67", "133"), "word", "word_soa_proportion")
      kl_133_267 <- compute_kl(NULL, word_prop_df, c("133", "267"), "word", "word_soa_proportion")
      kl_67_267 <- compute_kl(NULL, word_prop_df, c("67", "267"), "word", "word_soa_proportion")

      kl_divergence_df <- rbind(kl_divergence_df, data.frame(img_id = current_img_id,
                                                             experiment_no = exp_id,
                                                             soa_kl_67_133 = kl_67_133,
                                                             soa_kl_133_267 = kl_133_267,
                                                             soa_kl_67_267 = kl_67_267))
  }
  
  kl_divergence_df = data.table(img_id = kl_df$img_id, soa_kl_67_133 = kl_df$kl_67_133, soa_kl_133_267 = kl_df$kl_133_267, soa_kl_67_267 = kl_df$kl_67_267)
  return (kl_divergence_df)
}
```

```{r include=TRUE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}

### LAB BASED 5+5

library(arrangements)

d1_lb_df <- lab_raw_stem_df[experiment_no == 1, ][!img_id %in% c(3, 9, 14)][, agg_word := stem_word]
d1_mt_df <- mt_raw_stem_df[experiment_no == 1, ][!img_id %in% c(3, 9, 14)][, agg_word := stem_word]

# Re-sync stem-words across dataset (stem word is a combination)
all_images <- unique(d1_mt_df$img_id)

for (img in all_images) {
  for (s in c(67, 133, 267)) {
    lb_df <- d1_lb_df[img_id == img & soa == s]
    if (nrow(lb_df) > 0) {
      s1 <- stem_words(d1_mt_df[img_id == img & soa == s]$word)
      s2 <- stem_words(d1_lb_df[img_id == img & soa == s]$word)
      
      common_stem_words <- data.table(merge(s1, s2, by = c("stem_word"), all=FALSE))
      
      for (sw in unique(common_stem_words$stem_word)) {
        sw_df <- common_stem_words[stem_word == sw, c("word.x", "word.y")]
        combine_stem_words = paste0(unique(c(as.character(sw_df$word.x), as.character(sw_df$word.y))), collapse = ", ")
        
        d1_mt_df[img_id == img & soa == s & word %in% sw_df$word.x]$agg_word = combine_stem_words
        d1_lb_df[img_id == img & soa == s & word %in% sw_df$word.y]$agg_word = combine_stem_words
      }
    }
  }
}

ad1_lb_sbjs <- combinations(unique(d1_lb_df$subject), 10)
d1_mt_sbjs <- combinations(unique(d1_mt_df$subject), 10, nsample = 100)

#Pick random 50
# d1_lb_sbjs <- d1_lb_sbjs[sample(1:nrow(d1_lb_sbjs), 50), ]
# d1_mt_sbjs <- d1_mt_sbjs[sample(1:nrow(d1_mt_sbjs), 50), ]

#d4_lab_9_online_1_df <- data.table()
d1_online_10_online_10_df <- data.table()
mt_df <- data.table()
for (i in seq(from=1, to=nrow(d1_mt_sbjs), by=2)) {
    kl_df_1 <- calculate_kl_for_dataframe(d1_mt_df[subject %in% d1_mt_sbjs[i, ], ], FALSE, aggregate_word = FALSE)
    kl_df_2 <- calculate_kl_for_dataframe(d1_mt_df[subject %in% d1_mt_sbjs[i+1, ], ], FALSE, aggregate_word = FALSE)

    # Normalise the columns before we calculate KL divergence (need to sum up to 1)
    kl_total_word_soa_df <- kl_df_1[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
    kl_df_1 = merge(kl_df_1, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
    kl_df_1 <- kl_df_1[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "1"), by = c("img_id", "soa", "agg_word")]

    kl_total_word_soa_df <- kl_df_2[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
    kl_df_2 = merge(kl_df_2, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
    kl_df_2 <- kl_df_2[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "2"), by = c("img_id", "soa", "agg_word")]

    combine_kl_df <- rbind(kl_df_1, kl_df_2)

    ## Iterate through each images
    kl_stats_dt <- combine_kl_df[, .(kl = compute_kl_by_dataset(.BY, copy(.SD), c("1", "2") ,
                                                               "agg_word", "word_soa_proportion_norm", print_plot = FALSE)
    ), by = c("img_id", "soa")]

    kl_stats_dt <- cbind(kl_stats_dt, iteration = paste(c(d1_mt_sbjs[i, ], "|", d1_mt_sbjs[i+1, ]), collapse = ","))
    d1_online_10_online_10_df <- rbind(d1_online_10_online_10_df, kl_stats_dt)    
}

d1_lab_10_online_10_df <- data.table()
mt_df <- data.table()
for (i in seq(from=1, to=nrow(d1_mt_sbjs), by=1)) {
  
    kl_df_1 <- calculate_kl_for_dataframe(d1_lb_df[subject %in% d1_lb_sbjs, ], FALSE, aggregate_word = FALSE)
    kl_df_2 <- calculate_kl_for_dataframe(d1_mt_df[subject %in% d1_mt_sbjs[i, ], ], FALSE, aggregate_word = FALSE)

    # Normalise the columns before we calculate KL divergence (need to sum up to 1)
    kl_total_word_soa_df <- kl_df_1[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
    kl_df_1 = merge(kl_df_1, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
    kl_df_1 <- kl_df_1[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "1"), by = c("img_id", "soa", "agg_word")]

    kl_total_word_soa_df <- kl_df_2[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
    kl_df_2 = merge(kl_df_2, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
    kl_df_2 <- kl_df_2[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "2"), by = c("img_id", "soa", "agg_word")]

    combine_kl_df <- rbind(kl_df_1, kl_df_2)

    ## Iterate through each images
    kl_stats_dt <- combine_kl_df[, .(kl = compute_kl_by_dataset(.BY, copy(.SD), c("1", "2") ,
                                                               "agg_word", "word_soa_proportion_norm", print_plot = FALSE)
    ), by = c("img_id", "soa")]

    kl_stats_dt <- cbind(kl_stats_dt, iteration = paste(c(d1_lb_sbjs, "|", d1_mt_sbjs[i, ]), collapse = ","))
    d1_lab_10_online_10_df <- rbind(d1_lab_10_online_10_df, kl_stats_dt)    
}


plot_kl_compare(d1_online_10_online_10_df, d1_lab_10_online_10_df)

d1_lab_5_online_5_df = data.table()

for (i in 1:nrow(d1_lb_sbjs)) {
  # d1_mt_sbjs <- data.table(setdiff(unique(d1_lb_df$subject), d1_lb_sbjs[i,]))
  # d1_mt_sbjs <- dcast(d1_mt_sbjs, . ~ V1, value.var="V1")[,-(c("."))]

  for (j in 1:nrow(d1_mt_sbjs)) {
    temp_df <- rbind(
      d1_lb_df[subject %in% d1_lb_sbjs[i, ]],
      d1_mt_df[subject %in% d1_mt_sbjs[j, ]]
      #d1_lb_df[subject %in% d1_mt_sbjs[j, ]]
    )

    kl_df_1 <- calculate_kl_for_dataframe(d1_lb_df[subject %in% d1_lb_sbjs[i, ], ], FALSE, aggregate_word = FALSE)
    kl_df_2 <- calculate_kl_for_dataframe(d1_mt_df[subject %in% d1_mt_sbjs[j, ], ], FALSE, aggregate_word = FALSE)
    #kl_df_2 <- calculate_kl_for_dataframe(d1_lb_df[subject %in% d1_mt_sbjs[j, ], ], FALSE)

    # Normalise the columns before we calculate KL divergence (need to sum up to 1)
    kl_total_word_soa_df <- kl_df_1[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
    kl_df_1 = merge(kl_df_1, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
    kl_df_1 <- kl_df_1[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "1"), by = c("img_id", "soa", "agg_word")]

    kl_total_word_soa_df <- kl_df_2[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
    kl_df_2 = merge(kl_df_2, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
    kl_df_2 <- kl_df_2[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "2"), by = c("img_id", "soa", "agg_word")]

    ## Filter the larger dataset 1 to contain only SOA that matches smaller dataset 2
    # img_soa_df <- unique(kl_df_2[, c("img_id", "soa")])
    # kl_df_1 <- merge(kl_df_1, img_soa_df, by = c("img_id", "soa"))

    combine_kl_df <- rbind(kl_df_1, kl_df_2)

    ## Iterate through each images
    kl_stats_dt <- combine_kl_df[, .(kl = compute_kl_by_dataset(.BY, copy(.SD), c("1", "2") ,
                                                               "agg_word", "word_soa_proportion_norm", print_plot = FALSE)
    ), by = c("img_id", "soa")]

    kl_stats_dt <- cbind(kl_stats_dt, iteration = paste(c(d1_lb_sbjs[i, ], d1_mt_sbjs[j, ]), collapse = ","))
    d1_lab_5_online_5_df <- rbind(d1_lab_5_online_5_df, kl_stats_dt)
  }
}

save(d1_lab_5_online_5_df, file = "kl_divergence_d1_lab_5_online_5.RData")
```

```{r include=TRUE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}

### ONLINE BASED

# library(arrangements)
# 
# d1_lb_df <- lab_raw_stem_df[experiment_no == 1, ][!img_id %in% c(3, 9, 14)]
# d1_mt_df <- mt_raw_stem_df[experiment_no == 1, ][!img_id %in% c(3, 9, 14)]
# 
# d1_mt_sbjs <- combinations(unique(d1_mt_df$subject), length(unique(d1_mt_df$subject))-1)
# #d1_lb_sbjs <- combinations(unique(d1_lb_df$subject), 1)
# 
# d4_online_n_online_1_df <- data.table()
# 
# for (i in 1:nrow(d1_mt_sbjs)) {
#   d1_lb_sbjs <- data.table(setdiff(unique(d1_mt_df$subject), d1_mt_sbjs[i,]))
#     
#   for (j in 1:nrow(d1_lb_sbjs)) {
#     temp_df <- rbind(
#       d1_mt_df[subject %in% d1_mt_sbjs[i, ]],
#       d1_mt_df[subject %in% d1_lb_sbjs[j, ]]
#       #d1_lb_df[subject %in% d1_lb_sbjs[j, ]]
#     )
# 
#     kl_df_1 <- calculate_kl_for_dataframe(d1_mt_df[subject %in% d1_mt_sbjs[i, ], ], FALSE)
#     #kl_df_2 <- calculate_kl_for_dataframe(d1_lb_df[subject %in% d1_lb_sbjs[j, ], ], FALSE)
#     kl_df_2 <- calculate_kl_for_dataframe(d1_mt_df[subject %in% d1_lb_sbjs[j, ], ], FALSE)
# 
#     # Normalise the columns before we calculate KL divergence (need to sum up to 1)
#     kl_total_word_soa_df <- kl_df_1[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
#     kl_df_1 = merge(kl_df_1, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
#     kl_df_1 <- kl_df_1[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "1"), by = c("img_id", "soa", "agg_word")]
#     
#     kl_total_word_soa_df <- kl_df_2[, .(total_word_soa_proportion = sum(word_soa_proportion)), by = c("img_id", "soa")]
#     kl_df_2 = merge(kl_df_2, kl_total_word_soa_df, all.x = TRUE, by = c("img_id", "soa"))
#     kl_df_2 <- kl_df_2[, .(word_soa_proportion_norm = word_soa_proportion/total_word_soa_proportion, dataset = "2"), by = c("img_id", "soa", "agg_word")]
# 
#     ## Filter the larger dataset 1 to contain only SOA that matches smaller dataset 2
#     img_soa_df <- unique(kl_df_2[, c("img_id", "soa")])
#     kl_df_1 <- merge(kl_df_1, img_soa_df, by = c("img_id", "soa"))
#     
#     combine_kl_df <- rbind(kl_df_1, kl_df_2)
#     
#     ## Iterate through each images
#     kl_stats_dt <- combine_kl_df[, .(kl = compute_kl_by_dataset(.BY, .SD, c("1", "2") , 
#                                                                "agg_word", "word_soa_proportion_norm",
#                                                                print_plot = TRUE)
#     ), by = c("img_id", "soa")] 
#    
#     kl_stats_dt <- cbind(kl_stats_dt, iteration = paste(c(d1_mt_sbjs[i, ], d1_lb_sbjs[j, ]), collapse = ","))
#     d4_online_n_online_1_df <- rbind(d4_online_n_online_1_df, kl_stats_dt)
#   }
# }

#save(d4_online_n_lab_1_df, file = "kl_divergence_d4_online_n_lab_1.RData")

```

```{r include=TRUE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}
plot_kl_compare <- function(lab_9_online_1_df, lab_9_lab_1_df, labels = c("1", "2")) {
  merge_df <- rbind(
    cbind(lab_9_online_1_df, type = labels[1]),
    cbind(lab_9_lab_1_df, type = labels[2])
  )
  
  # plot_df <- melt(data = merge_df, id.vars = c("img_id", "type"), measure.vars = c("soa_kl_67_133", "soa_kl_133_267", "soa_kl_67_267", "soa_kl_133_67", "soa_kl_267_133", "soa_kl_267_67"), variable.name = "soa_pairs", value.name = "kl_divergence")
  
  plot_df <- merge_df
  dodge <- position_dodge(width = 0.9)
  g <- ggplot(plot_df, aes(x = soa, y = kl, fill = type)) +
    #geom_violin() +
    geom_violin(position = dodge) +
    geom_boxplot(width=0.3, position = dodge, show.legend = FALSE) +
    scale_y_continuous(expand = c(0, 0), limits = c(0.2, 1.1)) +
  # scale_x_discrete(labels=c("67", "133", "267")) +
    xlab("Presentation Duration") +
    ylab("Jensen-Shannon Values") +
    scale_fill_brewer(palette="Spectral")

  t_67 <- compute_ks_test(merge_df, labels[1], labels[2], 67)
  t_133 <- compute_ks_test(merge_df, labels[1], labels[2], 133)
  t_267 <- compute_ks_test(merge_df, labels[1], labels[2], 267)
   
  print(t_67)
  print(t_133)

  # Perform ks-test on two distribution
  return (g)

}

compute_ks_test <- function(df, type1, type2, s) {
  return (ks.test(
    df[type == type1 & soa == s, ]$kl, 
    df[type == type2 & soa == s, ]$kl, 
    ))
}
```

```{r include=FALSE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}
# load(file = "kl_divergence_d1_lab_9_lab_1.RData")
# load(file = "kl_divergence_d2_lab_9_lab_1.RData")
# load(file = "kl_divergence_d3_lab_9_lab_1.RData")
# load(file = "kl_divergence_d4_lab_9_lab_1.RData")
# load(file = "kl_divergence_d1_lab_9_online_1.RData")
# load(file = "kl_divergence_d2_lab_9_online_1.RData")
# load(file = "kl_divergence_d3_lab_9_online_1.RData")
# load(file = "kl_divergence_d4_lab_9_online_1.RData")
# 
# remove_outlier <- function(d) {
#   return(d[!d$kl %in% boxplot.stats(d$kl)$out])
# }
# 
# # d1_lab_9_lab_1_df <- remove_outlier(d1_lab_9_lab_1_df)
# # d1_lab_9_online_1_df <- remove_outlier(d1_lab_9_online_1_df)
# # 
# # d2_lab_9_lab_1_df <- remove_outlier(d2_lab_9_lab_1_df)
# # d2_lab_9_online_1_df <- remove_outlier(d2_lab_9_online_1_df)
# # 
# # d3_lab_9_lab_1_df <- remove_outlier(d3_lab_9_lab_1_df)
# # d3_lab_9_online_1_df <- remove_outlier(d3_lab_9_online_1_df)
# # 
# # d4_lab_9_lab_1_df <- remove_outlier(d4_lab_9_lab_1_df)
# # d4_lab_9_online_1_df <- remove_outlier(d4_lab_9_online_1_df)
# 
# d1_plot <- plot_kl_compare(d1_lab_9_online_1_df, d1_lab_9_lab_1_df)
# #d1_plot <- plot_kl_compare(lab_9_online_1_df, lab_9_lab_1_df)
# d1_sig <- d1_plot + geom_signif(y_position=c(0, 1.05, 0), xmin=c(0, 1.8, 0), xmax=c(0, 2.2, 0), annotation=c("", "*", ""), tip_length=0)
# 
# d2_plot <- plot_kl_compare(d2_lab_9_online_1_df, d2_lab_9_lab_1_df)
# # d2_sig <- d2_plot + geom_signif(y_position=c(15.2, 15.2, 5), xmin=c(0.8, 1.8, 0), xmax=c(1.2, 2.2, 0), annotation=c("***", "*", ""), tip_length=0)
# 
# d3_plot <- plot_kl_compare(d3_lab_9_online_1_df, d3_lab_9_lab_1_df)
# d3_sig <- d3_plot + geom_signif(y_position=c(1.05, 0, 1.05), xmin=c(0.8, 0, 2.8), xmax=c(1.2, 0, 3.2), annotation=c("***", "", "*"), tip_length=0)
# 
# d4_plot <- plot_kl_compare(d4_lab_9_online_1_df, d4_lab_9_lab_1_df)
# d4_sig <- d4_plot + geom_signif(y_position=c(0, 1.05, 0), xmin=c(0, 1.8, 0), xmax=c(0, 2.2, 0), annotation=c("", "***", ""), tip_length=0)
# 
# g_all <- grid.arrange(
#   d1_sig + scale_fill_discrete(name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   d2_plot + scale_fill_brewer(palette="Accent", name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   d3_sig + scale_fill_brewer(palette="Paired", name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   d4_sig + scale_fill_brewer(palette="Set3", name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   nrow = 2, ncol = 2)
# 
# # g_all <- grid.arrange(
# #   d1_plot, 
# #   d2_plot,
# #   d3_plot, 
# #   d4_plot,
# #   nrow = 2, ncol = 2)
# 
# h <- 7
# ar <- 1.5
# ggsave(g_all, height=h, width= h*ar, filename = "comparison-lab-online-sampling.png")
# 

```

```{r include=FALSE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}
load(file = "kl_divergence_d1_online_n_online_1.RData")
load(file = "kl_divergence_d2_online_n_online_1.RData")
load(file = "kl_divergence_d3_online_n_online_1.RData")
load(file = "kl_divergence_d4_online_n_online_1.RData")
load(file = "kl_divergence_d1_online_n_lab_1.RData")
load(file = "kl_divergence_d2_online_n_lab_1.RData")
load(file = "kl_divergence_d3_online_n_lab_1.RData")
load(file = "kl_divergence_d4_online_n_lab_1.RData")

load(file = "kl_divergence_d1_lab_5_lab_5.RData")
load(file = "kl_divergence_d1_lab_5_online_5.RData")

plot_kl_compare(d1_lab_5_lab_5_df, d1_lab_5_online_5_df)

remove_outlier <- function(d) {
  return(d[!d$kl %in% boxplot.stats(d$kl)$out])
}

# d1_lab_9_lab_1_df <- remove_outlier(d1_lab_9_lab_1_df)
# d1_lab_9_online_1_df <- remove_outlier(d1_lab_9_online_1_df)
# 
# d2_lab_9_lab_1_df <- remove_outlier(d2_lab_9_lab_1_df)
# d2_lab_9_online_1_df <- remove_outlier(d2_lab_9_online_1_df)
# 
# d3_lab_9_lab_1_df <- remove_outlier(d3_lab_9_lab_1_df)
# d3_lab_9_online_1_df <- remove_outlier(d3_lab_9_online_1_df)
# 
# d4_lab_9_lab_1_df <- remove_outlier(d4_lab_9_lab_1_df)
# d4_lab_9_online_1_df <- remove_outlier(d4_lab_9_online_1_df)

label <- c("online_n-1_lab_1", "online_n-1_online_1")

d1_plot <- plot_kl_compare(d1_online_n_lab_1_df, d1_online_n_online_1_df, labels = label)
#d1_plot <- plot_kl_compare(lab_9_online_1_df, lab_9_lab_1_df)
d1_sig <- d1_plot + geom_signif(y_position=c(0, 1.05, 0), xmin=c(0, 1.8, 0), xmax=c(0, 2.2, 0), annotation=c("", "*", ""), tip_length=0)

d2_plot <- plot_kl_compare(d2_online_n_lab_1_df, d2_online_n_online_1_df, labels = label)
# d2_sig <- d2_plot + geom_signif(y_position=c(15.2, 15.2, 5), xmin=c(0.8, 1.8, 0), xmax=c(1.2, 2.2, 0), annotation=c("***", "*", ""), tip_length=0)

d3_plot <- plot_kl_compare(d3_online_n_lab_1_df, d3_online_n_online_1_df, labels = label)
d3_sig <- d3_plot + geom_signif(y_position=c(1.05, 0, 1.05), xmin=c(0.8, 0, 2.8), xmax=c(1.2, 0, 3.2), annotation=c("***", "", "*"), tip_length=0)

d4_plot <- plot_kl_compare(d4_online_n_lab_1_df, d4_online_n_online_1_df, labels = label)
d4_sig <- d4_plot + geom_signif(y_position=c(0, 1.05, 0), xmin=c(0, 1.8, 0), xmax=c(0, 2.2, 0), annotation=c("", "***", ""), tip_length=0)

# g_all <- grid.arrange(
#   d1_sig + scale_fill_discrete(name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   d2_plot + scale_fill_brewer(palette="Accent", name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   d3_sig + scale_fill_brewer(palette="Paired", name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   d4_sig + scale_fill_brewer(palette="Set3", name = "", labels=c("Lab_9_Lab_1", "Lab_9_Online_1")),
#   nrow = 2, ncol = 2)

g_all <- grid.arrange(
  d1_plot,
  d2_plot,
  d3_plot,
  d4_plot,
  nrow = 2, ncol = 2)

h <- 7
ar <- 1.5
ggsave(g_all, height=h, width= h*ar, filename = "comparison-online-lab-sampling-jensen-shannon.png")


```

```{r include=FALSE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}
plot_kl_dataset <- function (d) {
  no_of_iterations_to_run <- 50
  sample_subject_no <- 10

  mt_bootstrap_df <- data.table()

  for (i in 1:no_of_iterations_to_run) {
    kl_df <- calculate_rnd_kl_divergence(mt_raw_stem_df, d, sample_subject_no)
    kl_df <- cbind(kl_df, iteration = i)
    mt_bootstrap_df <- rbind(mt_bootstrap_df, kl_df)
  }
  
  lb_kl_df <- calculate_rnd_kl_divergence(lab_raw_stem_df, d, sample_subject_no)
  
  plot_df <- mt_bootstrap_df[, .(img_id, soa_kl_67_133, soa_kl_67_267, soa_kl_133_267)]
  plot_df <- melt(data = plot_df, id.vars = c("img_id"), measure.vars = c("soa_kl_67_133", "soa_kl_67_267", "soa_kl_133_267"), variable.name = "soa_pairs", value.name = "kl_divergence")
  
  lab_plot_df <- melt(data = lb_kl_df, id.vars = c("img_id"), measure.vars = c("soa_kl_67_133", "soa_kl_67_267", "soa_kl_133_267"), variable.name = "soa_pairs", value.name = "kl_divergence")
  
  t_67_133 <- ks.test(lb_kl_df$soa_kl_67_133, mt_bootstrap_df[, soa_kl_67_133, by = img_id]$soa_kl_67_133)
  t_133_267 <- ks.test(lb_kl_df$soa_kl_133_267, mt_bootstrap_df[, soa_kl_133_267, by = img_id]$soa_kl_133_267)
  t_67_267 <- ks.test(lb_kl_df$soa_kl_67_267, mt_bootstrap_df[, soa_kl_67_267, by = img_id]$soa_kl_67_267)
   
  warning(t_67_133$statistic)
  warning("\n")
  warning(t_67_133$p.value)
  warning("\n")
  warning(t_67_267$statistic)
  warning("\n")
  warning(t_67_267$p.value)
  warning("\n")
  warning(t_133_267$statistic)
  warning("\n")
  warning(t_133_267$p.value)

  comb_plot_df <- plot_df[, `:=` (type = 'mturk')]
  comb_plot_df <- rbind(comb_plot_df, lab_plot_df[, `:=` (type = 'lab')])
  
  dodge <- position_dodge(width = 0.8)
  violin_all <- ggplot(comb_plot_df, aes(x = soa_pairs, y = kl_divergence, fill = type)) +
    geom_violin(position = dodge) +
    geom_boxplot(width=0.3, position = dodge, show.legend = FALSE) +
    scale_x_discrete(labels=c("67-133", "67-267", "133-267")) +
    xlab("") +
    ylab("Jensen-Shannon Distance") +
    ggtitle(sprintf("Dataset %d (Lab=%d, Online=%d)", d, 
                    length(unique(lab_raw_stem_df[experiment_no == d]$subject)),
                    length(unique(mt_raw_stem_df[experiment_no == d]$subject)))) +
    scale_fill_brewer(palette="Spectral")
  
  return (violin_all)
}
```

```{r include=FALSE, warning=TRUE, info=FALSE, message=FALSE, echo=FALSE}
library(ggsignif)

#set.seed(12345)
#set.seed(12345)

p1 <- plot_kl_dataset(1)
p2 <- plot_kl_dataset(2)
p3 <- plot_kl_dataset(3)
p4 <- plot_kl_dataset(4)

p4_sig <- p4 + geom_signif(y_position=c(1.02, 1.02, 1.02), xmin=c(0.8, 1.8, 2.8), xmax=c(1.2, 2.2, 3.2), annotation=c("*", "*", "*"), tip_length=0)

theme_set(theme_cowplot())

g_all <- grid.arrange(
  p1 + scale_fill_discrete(name = "", labels=c("Lab", "Online")), 
  p2 + scale_fill_brewer(palette="Accent", name = "", labels=c("Lab", "Online")),
  p3 + scale_fill_brewer(palette="Paired", name = "", labels=c("Lab", "Online")), 
  p4_sig + scale_fill_brewer(palette="Set3", name = "", labels=c("Lab", "Online")) + scale_y_continuous(limits = c(0.4, 1.05)),
  nrow = 2, ncol = 2)

h <- 7
ar <- 1.5
ggsave(pp, height=h, width= h*ar, filename = "comparison-lab-online-violin-datasets-1.png")

```

## Goodness-of-fit test - Chi-squared

Bootstrapped results (50 iterations, randomly select 10 MTurk participants in each iteration).

```{r echo=FALSE, message=TRUE, warning=FALSE, fig.height=7, fig.width = 7*1.5}
plot_df <- mt_bootstrap_df[, .(img_id, soa_kl_67_133, soa_kl_133_267, soa_kl_67_267)]
plot_df <- melt(data = plot_df, id.vars = c("img_id"), measure.vars = c("soa_kl_67_133", "soa_kl_133_267", "soa_kl_67_267"), variable.name = "soa_pairs", value.name = "kl_divergence")

mt <- ggplot(plot_df, aes(x = kl_divergence, color = soa_pairs)) + geom_density() + xlab("KL Divergence") +
  ggtitle("MTurk Participants (Random 10 participants x 50)")

lab_plot_df <- melt(data = lb_kl_df, id.vars = c("img_id"), measure.vars = c("soa_kl_67_133", "soa_kl_133_267", 
"soa_kl_67_267"), variable.name = "soa_pairs", value.name = "kl_divergence")

comb_plot_df <- plot_df[, `:=` (type = 'mturk')]
comb_plot_df <- rbind(comb_plot_df, lab_plot_df[, `:=` (type = 'lab')])

dodge <- position_dodge(width = 0.8)
violin_all <- ggplot(comb_plot_df, aes(x = soa_pairs, y = kl_divergence, fill = type)) + 
  geom_violin(position = dodge) +
  geom_boxplot(width=0.3, position = dodge) +
  scale_x_discrete(labels=c("67-133", "133-267", "67-267")) +
  xlab("SOA Pairs") +
  ylab("KL Divergence Values") +
  ggtitle("Dataset 1") + 
  scale_fill_brewer(palette="Spectral")

lb <- ggplot(lab_plot_df, aes(x = kl_divergence, color = soa_pairs)) + geom_density() + xlab("KL Divergence") +
  ggtitle("Lab Participants")

g_all <- grid.arrange(
  mt, lb,
  nrow = 1, ncol = 2)

h <- 7
ar <- 1.5
ggsave(g_all, height=h, width= h*ar, filename = "comparison-lab-online-bootstrap-dataset-1.png")

h <- 7
ar <- 1.5
ggsave(violin_all, height=h, width= h*ar, filename = "comparison-lab-online-violin-dataset-1.png")

```


Calculate the median of MTurk participants and compare it with Lab participants using Goodness-of-Fit using Chi-squared.

```{r echo=TRUE, message=TRUE, warning=FALSE}
t_67_133 <- ks.test(lb_kl_df$soa_kl_67_133, mt_bootstrap_df[, soa_kl_67_133, by = img_id]$soa_kl_67_133)
t_133_267 <- ks.test(lb_kl_df$soa_kl_133_267, mt_bootstrap_df[, soa_kl_133_267, by = img_id]$soa_kl_133_267)
t_67_267 <- ks.test(lb_kl_df$soa_kl_67_267, mt_bootstrap_df[, soa_kl_67_267, by = img_id]$soa_kl_67_267)
 
t_67_133
t_133_267
t_67_267


```
